\chapter{Self reflection}
Since DAWN Aerospace is a young startup company, it meant that I had quite a lot of independence on the choice of tasks I had to perform and on how to perform these tasks. The advantage of this was that I got to practice my self managing skills quite a bit.  \\

I would say that my previous experience as a team leader within Delft Aerospace Rocket Engineering (\gls{dare}) definitely helped during the internship. For the past few years I have been responsible for managing the development of several subsytems and projects, most of these involving the development of several simulation tools and their respective pre-/post-processing code. I've also been involved in the development of a control system for one of the rockets. \\

This pre-exiting knowledge served as a basis for the tasks I ended up doing within DAWN. However the tasks involved new methods that I haven't come across before in DARE and despite having to learn the theory behind these methods during lectures, it became clear that in practice it is more difficult to implement them. So it was good to realise just how much actually implementing these methods and testing them can help in understanding their inner workings. \\

At the beginning it did take some time to get used to managing my self, as in how to choose a task to work on, where is work more urgently needed. but by the end of the project everything was clear and it became easier to take decisions with more confidence. \\

One thing I do regret about this internship was that, since DAWN is still a small startup, I did not really get the chance to work with a more experienced control engineer in the field. As in I did not really get to learn on how these kind of problems are solved in practice directly from those who have already solved them in the past. However I do believe that I did gain a lot of new valuable experiences and knowledge that I would not have gotten outside of DAWN. \\

One thing I know I can improve about my self is the communication with my colleges. In general it did go quite well, but I know I can improve the way in which I explain the work I'm doing, why it's needed and why I took certain decisions. \\

Before the internship I did not really think much of working for a startup company after my studies. I always though that it would be best to join a large, well established company to insure my financial security, specially for the first few years after my studies. However after this internship I realized, that if I would like to work on some project I could enjoy working on and have some independence on the decisions I make, then a startup could be good choice. This internship will definitely affect my decision on where to work after I graduate. \\

In general I'm satisfied with the results of the internship project. I do think I could have taken better decisions during the project and that I could have done more before if I had taken them. I also think that the goals I chose might have been a bit to ambitious is some aspects, and that I could have possibly done a better job if I had dropped some parts of the project.  
